---
title: "biostats"
author: "Yu An"
date: "2019-10-21"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
This dataset contains several people with their sexs, ages, heights and weights

```{r import 2 columns}
temp<-read.csv("data/biostats.csv")[,c('Age','Height..in.')]
head(temp)
```
```{r distribution of Age}
stat<-read.csv(file ="data/biostats.csv", row.names =1)
barplot(stat$Age, names.arg = stat$Name,
     xlab = "Name", ylab = "Age",
     main="Plot of Age")
```
```{r distribution of Height}
barplot(stat$Height..in., names.arg = stat$Name,
     xlab = "Name", ylab = "Height(in)",
     main="Plot of Height")
```
```{r scatterplot}
scatter.smooth(x=temp$Age, y=temp$Height..in., 
               xlab = "Age", ylab = "Height(in)", 
               main="Scatter Plot of Age and Height")
```
```{r simple linear regression}
linearMod <- lm(temp$Height..in.~temp$Age)
print(linearMod)
summary(linearMod)

```
The linear regression shows whether there's a relationship between Age and Height of biostats of people in the dataset. Under this case, p-value is `r anova(linearMod)$Pr[1]`, which is less than 0.05. It is a meaningful addition to my linear regression model, because it means the age and height are significantly related.

